---
title: "wordsearchr"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{wordsearchr}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

# Introduction

`{wordsearchr}` is a package that allows you to quickly make a traditional word search and style it nicely for printing. The only hard part will be coming up with the words for which to search!

# Getting Started

To get started with the package, install using `remotes`:

```{r eval=FALSE}
install.packages("remotes")

remotes::install_github(
  "adambushman/wordsearchr", 
  dependencies = TRUE, 
  build_vignettes = TRUE
)
```

Once installed, load the package using the `library` command below or reference individual components using the `::` framework:

```{r}
# Load the entire library into the session

library("wordsearchr")
```

You'll find helpful functions for generating word search components, rendering, and assembling the final product. Let's see how!

# Making a word search

Word searches a fun activity for any age. What isn't fun is making it from scratch. Good news is with `{wordsearchr}`, you'll never have to again! 

Getting started is as simple as storing the words we'd like for the search into a vector and calling `gen_word_search()`:

```{r}
words <- c("Hi", "Hello", "Howdy")

wordsearch <- gen_word_search(
  words, "easy", "raw"
)
```

The above produces a list object with two elements. 1) the "grid" (the area to search), 2) the "reference" (the words to find), and 3) the "solution" (data to highlight the solution).

We can create an "easy" word search where words are mapped reading "right", "bottom", or a combination. A "hard" word searches uses "left", "top", and their combinations. You can also specify "mix" to allow for any mapping.

The "raw" type gives us a word search that keeps the empty spaces so you can validate. When you're satisfied, you can convert to a "ready" wordsearch with `ready_wordsearch()`. Just pass the whole wordsearch object:

```{r}
ready_ws <- ready_wordsearch(wordsearch)
```

Alternatively, if no validation is necessary, just pass "ready" to the type parameter of `gen_word_search()` from the get go and receive a word search with randomly generated letters already occupying those empty spaces.

To render the data structure in a graphical format, we can call `build_wordsearch()`. We need only pass it our wordsearch object and it will do all the heavy lifting, making use use of the `{ggplot2}` and `{patchwork}` packages.

```{r}
p <- build_wordsearch(ready_ws)
p
```

And now, we have our completed word search. Well done!
